% Copyright (C) 2019-2021 by Cheng Xu <copyright@xuc.me>
% All Rights Reserved.

\documentclass{mycv}

\name[Cheng Xu]{Cheng Xu \small{Ph.D.}}
\address{2910 Virtual Way, Vancouver, BC V5M 0B2, Canada}
\email{contact@xuc.me}
\homepage{https://xuc.me}
\github{xu-cheng}
\linkedin{xu-cheng}

\begin{document}

\maketitle%

\begin{summary}
Experienced Staff Software Developer with a robust background in designing and implementing secure, high-performance database and blockchain systems. Proficient in database management, blockchain, cryptography, and information security, with a comprehensive history of impactful research in academic and professional settings. Known for exceptional coding skills and significant contributions to major open source projects.
\end{summary}

\section{Professional \\ Experience}

\subsection{Fortinet}[Vancouver, BC, Canada]
\begin{positions}
  \entry{Staff Software Developer}{Feb 2024~--~Present}
  \entry{Senior Software Developer}{Dec 2021~--~Jan 2024}
\end{positions}

\begin{itemize}
  \item Initiated and spearheaded the CASB (cloud access security broker) signature project, designing the signature schema and implementing a comprehensive pipeline for maintenance, testing, and deployment of CASB signatures.
  \item Developed tools for signature quality assurance, including linters and automated CI/CD systems. Collaborated effectively with cross-functional teams to integrate CASB signatures with backend matching engines, enhancing overall security solutions.
  \item Contributed to the maintenance and enhancement of IoT device detection systems, focusing on maintaining a known device database using advanced web crawling and LLM techniques, and managed Kubernetes clusters for project pipelines.
\end{itemize}

\subsection{Simon Fraser University}[Burnaby, BC, Canada]
\begin{positions}
  \entry{Visiting Post-doctoral Research Fellow}{Mar 2020~--~May 2022}
\end{positions}

\begin{itemize}
  \item Advisor: \href{https://sites.google.com/view/jpei/jian-peis-homepage}{Prof.~Jian Pei}
  \item Designed novel techniques to build next-generation high-performance blockchain systems.
  \item Developed a blockchain prototype in Rust (\url{https://github.com/hkbudb/slimchain}) to validate the effectiveness of the novel design.
\end{itemize}

\subsection{Hong Kong Baptist University}[Hong Kong]
\begin{positions}
  \entry{Senior Research Assistant / Post-doctoral Research Fellow}{Dec 2018~--~Apr 2021}
  \entry{Ph.D.\ Candidate}{Nov 2014~--~Feb 2019}
\end{positions}

\begin{itemize}
  \item Advisor: \href{https://www.comp.hkbu.edu.hk/~xujl}{Prof.~Jianliang Xu}
  \item Developed innovative algorithms and indexing methods for enhancing cloud-based query services, facilitating efficient and verifiable query processing in enterprise systems.
  \item Innovated novel techniques to enable integrity assured search in blockchain databases.
  \item Resulted to several high-impact research papers published in top-tier journals and conferences.
\end{itemize}

\subsection{Syracuse University}[Syracuse, NY, USA]
\begin{positions}
  \entry{Visiting Scholar}{Sep 2017~--~Dec 2017}
\end{positions}

\begin{itemize}
  \item Advisor: \href{https://tristartom.github.io}{Dr.~Yuzhe Tang}
  \item Designed and implemented a memory-access pattern secure software system on Intel SGX\@.
  \item Developed a dynamic program partitioning framework that supports a variety of external oblivious algorithms, optimizing for cache-miss efficiency.
\end{itemize}

\subsection{\href{https://brew.sh}{Homebrew~|~https://brew.sh}}[Hong Kong]
\begin{positions}
  \entry{Core Maintainer}{Feb 2015~--~Feb 2017}
\end{positions}

\begin{itemize}
  \item Served as a core maintainer for Homebrew, the most widely-used package manager on macOS\@.
  \item Led the implementation of many key enhancements including an improved tap system, the core/formulae separation, a sandboxing system, and a portable Ruby environment, along with numerous improvements and bug fixes.
\end{itemize}

\section{Education}

\subsection{Hong Kong Baptist University}[Hong Kong]
\vspace{-\parskip}%
\begin{itemize}[label={}]
  \item Ph.D.\ in Computer Science \printdate{Nov 2014~--~May 2019}
  \item Dissertation: \href{https://scholars.hkbu.edu.hk/en/studentTheses/authenticated-query-processing-in-the-cloud}{Authenticated Query Processing in the Cloud}
  \item Advisor: \href{https://www.comp.hkbu.edu.hk/~xujl}{Prof.~Jianliang Xu}
\end{itemize}

\subsection{Huazhong University of Science and Technology}[Wuhan, China]
\vspace{-\parskip}%
\begin{itemize}[label={}]
  \item Bachelor of Engineering in Electronics \& Information Engineering \printdate{Sep 2009~--~Jun 2014}
\end{itemize}

\section{Skills}

\begin{description}
  \item[Programming] C/C++, Rust, Java, Python, Ruby, Matlab, \LaTeX, Bash, Javascript
  \item[Tools] Docker, Kubernetes, Terraform, Vim, Tmux, Git, macOS, Linux
  \item[Languages] English, Mandarin
\end{description}

\section{Research \\ Interests}

\begin{itemize}
  \item Authenticated query processing for outsourcing cloud computing.
  \item Searchable blockchain with integrity assurance.
  \item Privacy preserving query processing and access control.
\end{itemize}

\section{Selected \\ Publications}%

\textbf{Complete List:}
\href{https://scholar.google.com/citations?user=DKG_JaAAAAAJ}{Google Scholar \textsf{\footnotesize [DKG\_JaAAAAAJ]}}%
{~~$\cdot$~~}%
\href{https://dblp.org/pers/hd/x/Xu_0004:Cheng}{DBLP \textsf{\footnotesize [Xu\_0004:Cheng]}}%

\publications[keyword={selected}]{publications.bib}

% {
% \footnotesize%
% \textsuperscript{\textdagger}These authors contributed equally.
% }

\section{Talks}

\begin{enumerate}
  \item Blockchain Privacy Preserving Techniques, \emph{The 36th CCF National Database Conference}, Jinan, China, Oct.~2019.
  \item Towards Searchable and Verifiable Blockchain, \emph{1st Workshop on Blockchain and Data Management at 35th IEEE International Conference on Data Engineering}, Macau, Apr.~2019.
\end{enumerate}

\section{Awards}

\begin{itemize}
  \item SIGMOD Travel Award, ACM \printdate{2018}
  \item Department RPg Performance Award, Hong Kong Baptist University \printdate{2018,~2019}
  \item Yakun Scholarship Scheme for Mainland Postgraduate Students, Hong Kong Baptist University \printdate{2018}
\end{itemize}

\end{document}
